Programming Language Foundations in Agda

### 2019-07-16 papers/scp/PLFA.tex
Minor edit to SCP paper

(Before the release of Agda 2.6, Agda did not support highlighting embedded
literate code using HTML.  To address this, we wrote \texttt{agda2html}, a tool
which rewrote the output of Agda's HTML highlighter to accomplish this. This
tool had much more functionality, including the fixing of links as outlined
above, the stripping of implicit arguments to achieve a Haskell-like look, and
the support for new Markdown constructs for linking to Agda names. However,
Agda 2.6 has incorporated almost all of this functionality.)

>>>>

(Before the release of Agda 2.6, Agda did not support highlighting embedded
literate code in HTML.  We maintained \texttt{agda2html}, a tool which rewrites
the output of Agda's HTML highlighter to highlight embedded code. The tool had
much more functionality, including the fixing of links as outlined above, the
stripping of implicit arguments to achieve a Haskell-like look, and the support
for new Markdown constructs for linking to Agda names. However, Agda 2.6 has
incorporated almost all of this functionality, and \texttt{agda2html} is now
deprecated.)
